Malacology: A Programmable Storage System Built on Ceph

### 2016-05-10 paper/paper.tex
typo
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>
clarify
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

Briefly described in Section~\section{sec:intro}, Ceph supports the creation
of application-specific object interfaces~\cite{weil_rados_2007}. The ability
to offload computation can reduce data movement, and transactional interfaces can
significantly simplify construction of complex storage interfaces that require
uncoordinated parallel access.

@@

All of these modifications work in tandem to implement the desired behavior,
and are typically co-designed together such that each depends on the other to
behave as expected. In highly dynamic environments such as a distributed
storage system, changes to the system propagate at variable rates, requiring
all components of the system to be able to adapt. Thus, system services
realized through extensibility should be versioned together as a group,
exposing the version to allow introspection and domain-specific treatment of
version mismatch scenarios.

>>>>

Briefly described in Section~\ref{sec:intro}, Ceph supports the creation
of application-specific object interfaces~\cite{weil_rados_2007}. The ability
to offload computation can reduce data movement, and transactional interfaces can
significantly simplify construction of complex storage interfaces that require
uncoordinated parallel access.

@@

{\bf Interface management.} All of these modifications work in tandem to
implement the desired behavior, and are typically co-designed together such
that each depends on the other to behave as expected. In highly dynamic
environments such as a distributed storage system, changes to the system
propagate at variable rates, requiring all components of the system to be able
to adapt. Thus, system services realized through extensibility should be
versioned together as a group, exposing the version to allow introspection and
domain-specific treatment of version mismatch scenarios.
